\documentclass[12pt,a4paper]{moderncv}
\moderncvtheme[purple]{classic}
\usepackage[utf8]{inputenc}
\usepackage[inline]{enumitem}
% Marge aux 4 coins de la page, ici elles sont réduites pour gagner de la place
\usepackage[top=1.2cm, bottom=1.2cm, left=1.5cm, right=1.5cm]{geometry}
% Largeur de la colonne de gauche pour les dates
\setlength{\hintscolumnwidth}{2.7cm}
\firstname{Antoine}
\familyname{MORRIER}
\title{C++ Software Engineer}
%\address{2 rue qui n'existe pas}{63000 Clermont-Ferrand}
\email{antoine@morria.tech}
\homepage{cpp-rendering.io}
\mobile{+33 6 63 97 04 67}
\social[github]{qnope}
\social[twitter]{cpp-rendering}
\extrainfo{31 years old -- Driving licence}

% bibliography adjustments (only useful if you make citations in your resume, or print a list of publications using BibTeX)
%   to show numerical labels in the bibliography (default is to show no labels)
%\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}
%   to redefine the bibliography heading string ("Publications")
%\renewcommand{\refname}{Articles}

% bibliography with multiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\vspace{-3em}

\section{Experience}

\cventry{2023--Present}{Freelance Software Developer}{}{Montpellier}{}{
Modern C++, Qt/QML, Workshops, Training, Consulting, and Software Architecture.
\newline
Organizer of the C++ Meetup Montpellier
\newline
Writing articles about C++ and rendering on my blog: \href{https://cpp-rendering.io}{cpp-rendering.io}.
\begin{itemize}%
  \itemsep0em
  \item \textbf{SLB (Schlumberger, 2023--Present)}: Techlog Team%
  \newline
  Techlog is a market-leading digital solution for the wellbore industry.
  It is used by geologists and petrophysicists. Working within a team of 30 people, I achieved
  the following.
    \begin{itemize}[itemsep=0em, topsep=0em, leftmargin=1em]
      \item Designed a compile-time guaranteed thread-safe framework.
      \item Refactored core components of the Techlog software.
      \item Improved overall performance.
      \item Delivered workshops and training sessions to present new modern C++ features and show how they can be applied to make the codebase simpler and more efficient.
    \end{itemize}
  \item \textbf{Diagdev (2025--2 months)}: Developer team%
  \newline
  For a one-time need, Diagdev called upon my services to help with various aspects, such as bug fixing and improving compilation times. Compilation times were the main focus of my assignment, as resource consumption during compilation rendered the computer unusable. Results:
  \begin{itemize}[itemsep=0em, topsep=0em, leftmargin=1em]
    \item 22 minutes to 9 minutes for a full build.
    \item Faster incremental builds (as fewer files need to be recompiled).
    \item Estimated gain: 0.8 days per week per developer.
    \item Some bugs fixed.
  \end{itemize}
\end{itemize}
Used technologies: C++, Qt, OpenGL, Vulkan, QML, QtQuick
}

\cventry{2019--2023}{C++ Software Engineer}{Diagdev}{Castries}{}{
Diagdev is an engineering firm that designs machines related to hematology. The company is made up of around forty people from various backgrounds: electronics engineers, developers, mechanical engineers... The development team consists of 5 people. The projects I was assigned to were
\begin{itemize}[label=\labelitemii]%
  \itemsep0em
  \item A slide stainer: used to stain slides to help biologists perform manual cell counting.
  \item A blood analyzer: from a tube of blood, it extracts the blood formula (red blood cells, white blood cells).
\end{itemize}
My tasks were:
\begin{itemize}[label=\labelitemii]%
  \itemsep0em
  \item Worked with modern C++ (C++17) and Qt5 Framework on Hematology-related devices.
  \item Built a variant-based message communication with the underlying micro-controllers.
  \item Implemented tools to reduce boilerplate in interactions between C++ code and QML.
  \item Participated in the development of the blood cell classification algorithm.
  \item Presented modern C++ features to the team.
\end{itemize}
Used technologies: C++, Python, QML, Qt, QtQuick
}

\vspace{0.5em}
\cventry{2017--2018}{C++ Software Engineer}{Ausy / Airbus}{Sophia Antipolis}{}{
Airbus Defence and Space develops Pixel Factory, a software solution for analyzing satellite images or aerial views (for example, from an aircraft). I was assigned to the team developing visualization software for bundle adjustment results. From control points extracted from satellite images, we would locate them in the associated 3D model. We were 2 developers, plus a project manager.
\begin{itemize}[label=\labelitemii]
  \itemsep0em
  \item Worked on software for search and visualization of tie points and ground control points on drone, aerial, and satellite imagery for 3D modeling and mapping.
  \item Developed and integrated multithreaded modules, user interfaces, and services for projection between different geodetic systems.
  \item Developed new track visualization and non-geolocated 3D model visualization features.
\end{itemize}
Used technologies: C++, Qt
}

\cventry{2017}{Temporary Instructor}{Télécom SudParis}{Evry}{}{
  \begin{itemize}[label=\labelitemii]
    \itemsep0em
    \item Created and delivered a complete modern OpenGL course for engineering students at Télécom SudParis and ENSIIE.
\end{itemize}
}

\section{Education}
\cventry{2014--2018}{Engineering student}{Télécom SudParis}{Evry, France}{}{
  \begin{itemize}[label=\labelitemii]
    \itemsep0em
    \item High-Tech Imaging: specialization in image processing.
  \end{itemize}
}

\section{Skills}
\cvdoubleitem{\textbf{Languages}}{C++ 26, QML, Rust}{\textbf{Framework}}{Qt and QtQuick}
\cvdoubleitem{\textbf{Rendering}}{OpenGL 4+ / Vulkan}{\textbf{GPGPU}}{GLSL(Compute Shaders)}
\cvitem{\textbf{Miscellaneous}}{CMake, Git}

\section{Interests}
\cvdoubleitem{\textbf{Cars}}{Track driving}{\textbf{Science}}{Maths, Physics}
\end{document}
